Motorcycle Acceleration example

### 2020-06-24 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

This is an illustration of "smoothing via adaptive shrinkage" (SMASH)
applied to the Motorcycle Accident data. This implements the
"illustrative application" presented in Sec. 5.1 of the manuscript.

@@

Load the MASS, lattice wavethresh, EbayesThresh and smashr
packages. The MASS package is loaded only for the Motorcycle Accident
data. Some additional functions are defined in file
`motorcycle.functions.R`.

@@

Apply SMASH to the Motorcycle Accident data set.

@@

Create a plot showing the Motorcycle Accident data and the smash
estimates (with the dashed red lines showing the confidence
intervals).

@@

Apply SMASH, this time assuming equal variances, to the Motorcycle
Accident data set:

@@

Apply TI thresholding to the Motorcycle Accident data
-----------------------------------------------------

Apply TI thresholding to the Motorcycle Accident data set. In this
first run, the variance is assumed to be constant.

@@

Apply TI thresholding to the Motorcycle Accident data, this time using
the variances estimated using the "median absolute deviation", or
RMAD, method.

@@

Apply TI thresholding to the Motorcycle Accident data, this time using
the variances estimated by SMASH.

>>>>

This is an illustration of "smoothing via adaptive shrinkage" (SMASH)
applied to the Motorcycle Acceleration data. This implements the
"illustrative application" presented in Sec. 5.1 of the manuscript.

@@

Load the MASS, lattice wavethresh, EbayesThresh and smashr
packages. The MASS package is loaded only for the Motorcycle Acceleration
data. Some additional functions are defined in file
`motorcycle.functions.R`.

@@

Apply SMASH to the Motorcycle Acceleration data set.

@@

Create a plot showing the Motorcycle Acceleration data and the smash
estimates (with the dashed red lines showing the confidence
intervals).

@@

Apply SMASH, this time assuming equal variances, to the Motorcycle
Acceleration data set:

@@

Apply TI thresholding to the Motorcycle Acceleration data
-----------------------------------------------------

Apply TI thresholding to the Motorcycle Acceleration data set. In this
first run, the variance is assumed to be constant.

@@

Apply TI thresholding to the Motorcycle Acceleration data, this time using
the variances estimated using the "median absolute deviation", or
RMAD, method.

@@

Apply TI thresholding to the Motorcycle Acceleration data, this time using
the variances estimated by SMASH.
